Predicting computational reproducibility of scientific pipelines using collaborative filtering

### 2018-05-07 paper.tex
Some fixes following meeting

TP: The number of cases correctly predicted as occurance of difference \\
FP: The number of cases incorrectly predicted as occurance of difference \\
TN: The number of cases correctly predicted as no occurance of difference \\ 
FN: The number of cases incorrectly predicted as no occurance of difference \\
\[
	    Accuracy = \frac{TP+TN}{TP+TN+FP+FN}
\]
Sensitivity: The ability to predict the differences cases correctly. The bellow formula can be used to calculate sensitivity of a test.
\[
            Sensitivity = \frac{TP}{TP+FN}
\]
Specificity: The ability to predict the non differences cases correctly. The following formula can be used to calculate specificity of a test. 
\[
            Specificity = \frac{TN}{TN+FP}
\]

The experimental results have been obtained from four different approaches:\\
1. Applying ALS technique (ALS)\\
2. Employing Bias as well as ALS technique (ALS-Bias)\\
3. Using just Bias (Bias)\\
4. Results stemmed from ommiting the impact of predicted value of canstant files \\
In all above approaches, dummy classifier which makes prediction by using simple rules\cite{URL}
has been used to indicate that how much the predicted value would tend to be anticipate 
as the dominent value of the utility matrix. This classifier is considered as an 
accuracy evaluator since the binary utility matrix is consist of \{1,0\} which  
respectively represent whether a difference has been observed between the same files 
in two different conditions (by comapring their checksums) or not.
With the knowledge of the fact that Random Unreal method is not applicable into our 
case study, we used its results as the comparision between the unrealistic method 
and realistics ones. In this regard, the aformentioned approaches are propossed and 
tried to lessen the gaps between the best results from random-unreal and the applied one.

\subsection{ALS without biases}
In this phase of the experiment, the Alternating Least Squares techniq of Collaborative Filtering is applied for all provided methods. \todo{should I talk about ALS in here?}
Figure~\ref{fig:ALS-Failure} represents
The accuracy graph of four diferent Complete Columns, RS, Complete Rows and Random Unreal methods.The comparision to dummy
classifier over the increasement of the training ratio can be seen in this figure.
\begin{figure}[h!]
        \centering
        \begin{subfigure}[b]{0.8\linewidth}
                \includegraphics[width=\columnwidth]{figures/ALS/AlS-Failure-5vs6}
        \end{subfigure}
        \begin{subfigure}[b]{0.8\linewidth}
                \includegraphics[width=\columnwidth]{figures/ALS/AlS-Failure-5vs7}
        \end{subfigure}
        \begin{subfigure}[b]{0.8\linewidth}
                \includegraphics[width=\columnwidth]{figures/ALS/AlS-Failure-6vs7}
        \end{subfigure}
        \caption{Average performance of Complete Columns, RS, Complete Rows and Random Unreal methods in three different condition pairs}
        \label{fig:ALS-Failure}
\end{figure}

\subsubsection{Random Unreal}
This method has a great performance with absolute accouracy of more than $0.95$ 
even by accessing to small taining size of 10 percent. As it mentioned earlier 
this method is not applicable in pipline due to timestamp cosideration but it 
is a good criteria to estmiate the performance of other methods and try to modify 
the proposed methods in order to their accuracy be as colsed as possible to the 
Random Unreal method ones.

\subsubsection{Complete Columns}
As it shown in Figure~\ref{fig:ALS-Failure} the Complete Columns method has
almost a constant accuracy even if the training ratio increased and it
is almost two times less than dummy classifier in more differentiated
condition pairs (CentOS5 vs CentOS7 and CentOS6 vs CentOS7). But in the
best case which it means in similar conditions the Complete Columns
accuracy is as much accurate as the Dummy classifier which is $0.65$
percent.
\\
\subsubsection{Complete Rows}
As it can be observed, Figure~\ref{fig:ALS-Failure}, This method has some 
flactuation over the gowth of training set size. These falactuations are more 
frequent in condition pairs which have higher difference positive ratio. 
Also by enlarging the training ratio specially between $0.3$ to $0.7$, 
we can see dummy classifier has better results than Complete Rows ones. 
In other words despite of better performance of Complete Rows than 
dummy classifier at the last 10 percent of the graph, its accuracies 
are less than dummy classifiers ones.  
\\
\subsubsection{Random Subjects-RS}
The performance of RS method is represented in Figure~\ref{fig:ALS-Failure}.
Same to the Complete Row method, RS method has some flactuation but not as frequent 
as Complete Rows method. Althogh there are some up and down trends specialy with 
training ratio range of $0.2$ to $0.6$ but its constant growth trend after 
training ratio $0.3$ in condition pairs with high difference positive ratio is considerable.
The method can be $0.99$ percent accurate when it has over 70 percent of the data however 
this accuracy can be achived with higher training ratio (over 80 percent) for C5C6.  
\\
\\
\noindent Figure~\ref{fig:ALS-Succeed} represents
the accuracy graph of all Random kind methods with comparision to dummy
classifier over the increasement of the training ratio.\\
\begin{figure}[h!]
        \centering
        \begin{subfigure}[b]{0.8\linewidth}
                \includegraphics[width=\columnwidth]{figures/ALS/ALS-Succeed-5vs6}
        \end{subfigure}
        \begin{subfigure}[b]{0.8\linewidth}
                \includegraphics[width=\columnwidth]{figures/ALS/ALS-Succeed-5vs7}
        \end{subfigure}
        \begin{subfigure}[b]{0.8\linewidth}
                \includegraphics[width=\columnwidth]{figures/ALS/ALS-Succeed-6vs7}
        \end{subfigure}
        \caption{Average performance of RFNU methods in three different condition pairs}
        \label{fig:ALS-Succeed}
\end{figure}
\subsubsection{Random File Numbers(Uniform) - RFNU}
The continuous rise of RFNU accuracy trend can be observed in Figure~\ref{fig:ALS-Succeed}.
However a 0.03 drop is recorded in C6C7 between training ratio size of $0.8$ to $0.9$. 
This method takes over the dummy accuracy after having a training size more than 40 percent 
in condition pairs of C5vsC7 and C6vsC7 but it always shows better acuracy than 
dummy classifier ($0.73$ percent with traininfg ratio of $0.1$).

>>>>

Four experiments have been conducted to evaluate the performance of our 
predictions using (1) ALS without biases, (2) ALS with biases, (3) Biases only. 
Results will be evaluated on the complete datasets and specifically on the files that
do not behave consistently across subjects (\todo{explain this in introduction}).

We evaluate prediction methods using accuracy, sensitivity and specificity defined as follows:
\[
        Accuracy = \frac{TP+TN}{TP+TN+FP+FN}
\]
\[
        Sensitivity = \frac{TP}{TP+FN}
\]
\[
        Specificity = \frac{TN}{TN+FP}
\]
Where TP is the number of True Positives (correctly predicted errors), 
FP is the number of False Positives, TN is the number of true negatives 
and FN is the number of false negatives.

We compare our methods to two references, (1) a dummy classifier that always predicts the dominant class.
as the dominent value of the utility matrix (1 or 0), (2) the Random Unreal method, used as the baseline sampling technique.

\subsection{ALS without biases}
In this phase of the experiment, the Alternating Least Squares 
technique of Collaborative Filtering is applied for all provided 
methods. Our four sampling techniques are compared in 
Figure~\ref{fig:ALS-Failure} and the results are described in the next 
sub-sections.

\begin{figure}[h!]
        \centering
        \begin{subfigure}[b]{0.8\linewidth}
                \includegraphics[width=\columnwidth]{figures/ALS/AlS-Failure-5vs6}
        \end{subfigure}
        \begin{subfigure}[b]{0.8\linewidth}
                \includegraphics[width=\columnwidth]{figures/ALS/AlS-Failure-5vs7}
        \end{subfigure}
        \begin{subfigure}[b]{0.8\linewidth}
                \includegraphics[width=\columnwidth]{figures/ALS/AlS-Failure-6vs7}
        \end{subfigure}
        \caption{Average accuracy of Complete Columns, RS, Complete Rows and Random Unreal methods in three different condition pairs.}
        \label{fig:ALS-Failure}
\end{figure}

\subsubsection{Random Unreal}
This method has a great performance with absolute accuracy of more than $0.95$ 
even by accessing to small training size of 10 percent. As it mentioned earlier 
this method is not applicable in pipline due to timestamp consideration but it 
is a good criteria to estimate the performance of other methods and try to modify 
the proposed methods in order to their accuracy be as closed as possible to the 
Random Unreal method ones.

\subsubsection{Complete Columns}
The Complete Columns method has
almost a constant accuracy even if the training ratio increased and it
is almost two times less than dummy classifier in more differentiated
condition pairs (CentOS5 vs CentOS7 and CentOS6 vs CentOS7). But in the
best case which it means in similar conditions the Complete Columns
accuracy is as much accurate as the Dummy classifier which is $0.65$
percent.
\\
\subsubsection{Complete Rows}
This method has some 
flactuation over the gowth of training set size. These falactuations are more 
frequent in condition pairs which have higher difference positive ratio. 
Also by enlarging the training ratio specially between $0.3$ to $0.7$, 
we can see dummy classifier has better results than Complete Rows ones. 
In other words despite of better performance of Complete Rows than 
dummy classifier at the last 10 percent of the graph, its accuracies 
are less than dummy classifiers ones.  
\\
\subsubsection{Random Subjects-RS}
Same to the Complete Row method, RS method has some flactuation but not as frequent 
as Complete Rows method. Althogh there are some up and down trends specialy with 
training ratio range of $0.2$ to $0.6$ but its constant growth trend after 
training ratio $0.3$ in condition pairs with high difference positive ratio is considerable.
The method can be $0.99$ percent accurate when it has over 70 percent of the data however 
this accuracy can be achived with higher training ratio (over 80 percent) for C5C6.  
\\
\\
\noindent Figure~\ref{fig:ALS-Succeed} represents
the accuracy graph of all Random kind methods with comparision to dummy
classifier over the increasement of the training ratio.\\
\begin{figure}[h!]
        \centering
        \begin{subfigure}[b]{0.8\linewidth}
                \includegraphics[width=\columnwidth]{figures/ALS/ALS-Succeed-5vs6}
        \end{subfigure}
        \begin{subfigure}[b]{0.8\linewidth}
                \includegraphics[width=\columnwidth]{figures/ALS/ALS-Succeed-5vs7}
        \end{subfigure}
        \begin{subfigure}[b]{0.8\linewidth}
                \includegraphics[width=\columnwidth]{figures/ALS/ALS-Succeed-6vs7}
        \end{subfigure}
        \caption{Average performance of RFNU methods in three different condition pairs}
        \label{fig:ALS-Succeed}
\end{figure}
\subsubsection{Random File Numbers(Uniform) - RFNU}
The continuous rise of RFNU accuracy trend can be observed in Figure~\ref{fig:ALS-Succeed}.
However a 0.03 drop is recorded in C6C7 between training ratio size of $0.8$ to $0.9$. 
This method takes over the dummy accuracy after having a training size more than 40 percent 
in condition pairs of C5vsC7 and C6vsC7 but it always shows better acuracy than 
dummy classifier ($0.73$ percent with traininfg ratio of $0.1$).
